Location and Scale-Invariant Power Transformations for Transforming Data to

### 2025-04-03 manuscript_rmarkdown/manuscript.Rmd
Update weights in table.

\midrule
non-robust               & ---  & ---       & ---  & ---  & ---       & ---  & 4.98 \\
$p^{*}$ (step)           & 0.80 & $(0, 1]$  & 0.75 & ---  & ---       & ---  & 2.83 \\
$p^{*}$ (triangle)       & 0.80 & $(0, 1]$  & 0.00 & 0.95 & $(0, 1]$  & 0.82 & 2.63 \\
$p^{*}$ (tapered cosine) & 0.80 & $(0, 1]$  & 0.00 & 0.95 & $(0, 1]$  & 0.89 & 2.63 \\
$z$ (step)               & 1.28 & $(0, 10]$ & 2.33 & ---  & ---       & ---  & 5.04 \\
$z$ (triangle)           & 1.28 & $(0, 10]$ & 0.20 & 1.96 & $(0, 10]$ & 4.90 & 4.96 \\
$z$ (tapered cosine)     & 1.28 & $(0, 10]$ & 1.22 & 1.96 & $(0, 10]$ & 5.12 & 5.23 \\
$r$ (step)               & 0.50 & $(0, 10]$ & 0.75 & ---  & ---       & ---  & 5.07 \\
$r$ (triangle)           & 0.50 & $(0, 10]$ & 0.83 & 1.00 & $(0, 10]$ & 0.84 & 5.18 \\
$r$ (tapered cosine)     & 0.50 & $(0, 10]$ & 0.75 & 1.00 & $(0, 10]$ & 0.76 & 5.11 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}

@@

\midrule
non-robust               & ---  & ---       & ---  & ---  & ---       & ---  & 5.09 \\
$p^{*}$ (step)           & 0.80 & $(0, 1]$  & 0.81 & ---  & ---       & ---  & 2.85 \\
$p^{*}$ (triangle)       & 0.80 & $(0, 1]$  & 0.00 & 0.95 & $(0, 1]$  & 0.83 & 2.46 \\
$p^{*}$ (tapered cosine) & 0.80 & $(0, 1]$  & 0.04 & 0.95 & $(0, 1]$  & 0.88 & 2.45 \\
$z$ (step)               & 1.28 & $(0, 10]$ & 3.32 & ---  & ---       & ---  & 4.50 \\
$z$ (triangle)           & 1.28 & $(0, 10]$ & 0.42 & 1.96 & $(0, 10]$ & 4.35 & 4.08 \\
$z$ (tapered cosine)     & 1.28 & $(0, 10]$ & 0.53 & 1.96 & $(0, 10]$ & 5.08 & 4.18 \\
$r$ (step)               & 0.50 & $(0, 10]$ & 1.05 & ---  & ---       & ---  & 5.79 \\
$r$ (triangle)           & 0.50 & $(0, 10]$ & 1.04 & 1.00 & $(0, 10]$ & 1.09 & 5.89 \\
$r$ (tapered cosine)     & 0.50 & $(0, 10]$ & 1.07 & 1.00 & $(0, 10]$ & 1.08 & 5.81 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}

>>>>

\midrule
non-robust               & ---  & ---       & ---  & ---  & ---       & ---  & 6.06 \\
$p^{*}$ (step)           & 0.80 & $(0, 1]$  & 0.81 & ---  & ---       & ---  & 3.16 \\
$p^{*}$ (triangle)       & 0.80 & $(0, 1]$  & 0.00 & 0.95 & $(0, 1]$  & 0.86 & 2.93 \\
$p^{*}$ (tapered cosine) & 0.80 & $(0, 1]$  & 0.00 & 0.95 & $(0, 1]$  & 0.90 & 2.96 \\
$z$ (step)               & 1.28 & $(0, 10]$ & 2.33 & ---  & ---       & ---  & 6.21 \\
$z$ (triangle)           & 1.28 & $(0, 10]$ & 0.09 & 1.96 & $(0, 10]$ & 4.92 & 6.15 \\
$z$ (tapered cosine)     & 1.28 & $(0, 10]$ & 1.88 & 1.96 & $(0, 10]$ & 3.43 & 6.68 \\
$r$ (step)               & 0.50 & $(0, 10]$ & 0.75 & ---  & ---       & ---  & 6.25 \\
$r$ (triangle)           & 0.50 & $(0, 10]$ & 0.83 & 1.00 & $(0, 10]$ & 0.84 & 6.47 \\
$r$ (tapered cosine)     & 0.50 & $(0, 10]$ & 0.75 & 1.00 & $(0, 10]$ & 0.76 & 6.28 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}

@@

\midrule
non-robust               & ---  & ---       & ---  & ---  & ---       & ---  & 6.19 \\
$p^{*}$ (step)           & 0.80 & $(0, 1]$  & 0.81 & ---  & ---       & ---  & 3.13 \\
$p^{*}$ (triangle)       & 0.80 & $(0, 1]$  & 0.00 & 0.95 & $(0, 1]$  & 0.87 & 2.73 \\
$p^{*}$ (tapered cosine) & 0.80 & $(0, 1]$  & 0.14 & 0.95 & $(0, 1]$  & 0.91 & 2.80 \\
$z$ (step)               & 1.28 & $(0, 10]$ & 3.32 & ---  & ---       & ---  & 5.50 \\
$z$ (triangle)           & 1.28 & $(0, 10]$ & 0.30 & 1.96 & $(0, 10]$ & 5.91 & 5.78 \\
$z$ (tapered cosine)     & 1.28 & $(0, 10]$ & 0.53 & 1.96 & $(0, 10]$ & 5.08 & 5.16 \\
$r$ (step)               & 0.50 & $(0, 10]$ & 1.05 & ---  & ---       & ---  & 7.51 \\
$r$ (triangle)           & 0.50 & $(0, 10]$ & 1.04 & 1.00 & $(0, 10]$ & 1.08 & 7.61 \\
$r$ (tapered cosine)     & 0.50 & $(0, 10]$ & 1.17 & 1.00 & $(0, 10]$ & 1.54 & 8.80 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}
